## This Notebook can be can be used for Ecommerce website A/B testing Analysis purposes

## Understing Data
```{r}
View(Test_Data)
names(Test_Data)
class(Test_Data)
mode(Test_Data)
str(Test_Data)
```

## A/B Test Summary results 
```{r}

install.packages("formattable")
install.packages("kableExtra")
library(kableExtra)
library(formattable)
library(tidyverse)

Test_Data %>% group_by(SPLIT_GROUP) %>% summarise(
  Start_Date = format(min(TEST_DATE), '%Y-%m-%d'), 
  End_Date = format(max(TEST_DATE), '%Y-%m-%d'),
  Test_Duration = n_distinct(format((TEST_DATE), '%Y-%m-%d')),
  Sessions = comma(n_distinct(SESSION_ID),digit = 0), 
  Total_Sales = sum(SALES),
  Total_Orders = sum(ORDERS),
  CVR = formattable::percent(sum(ORDERS)/n_distinct(SESSION_ID)), 
  AOV= round(sum(SALES)/sum(ORDERS),2),
  RPS = round(sum(SALES)/n_distinct(SESSION_ID),2)
  ) %>% 
  kbl()%>%kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```

##Lift Calculations
```{r}
RPS_Lift <- percent((((Test_Data%>%  summarise(t_sales = mean(case_when(SPLIT_GROUP == "TEST" ~ SALES), na.rm=TRUE)))/
(summarise(Test_Data,t_sales = mean(case_when(SPLIT_GROUP == "CONTROL" ~ SALES), na.rm=TRUE))))-1),2)

```


## Trend Chart for CVR 
```{r}
Test_Data %>% mutate(TEST_DATE_1 = format(TEST_DATE, '%Y-%m-%d')) %>% 
  group_by(TEST_DATE_1, SPLIT_GROUP) %>%
  summarise(Daily_Sales = sum(SALES),
           Daily_Orders = sum(ORDERS), 
           CVR = sum(SALES)/sum(ORDERS)) %>% 
  ggplot(aes(TEST_DATE_1, CVR, group = SPLIT_GROUP, col = SPLIT_GROUP))+
  geom_line()
```

## Statistical significance for Sales
```{r}
 t.test(filter(Test_Data, SPLIT_GROUP=="CONTROL")$SALES,filter(Test_Data, SPLIT_GROUP=="TEST")$SALES, 
 alternative= "two.sided",paired = FALSE)
```

## Scatter Plot 
```{r}
Test_Data %>% ggplot(aes(ORDERS,SALES))+
  geom_point( aes(colour = SPLIT_GROUP,shape = SPLIT_GROUP))+
  labs(title="Scatter Plot")
```

## Box Plot 
```{r}
Test_Data %>% filter(SALES > 0 )%>%ggplot(aes(SPLIT_GROUP, SALES))+
  geom_boxplot()+
  scale_y_continuous(trans = "log2")
```




---
title: "AB Test Measurement Analysis"
output: html_notebook
---

## load libraries 
```{r}
library(tidyverse)
library(lubridate)
install.packages("formattable")
library(formattable)
```


##Load Data thats dowloaded from Kaggle  

```{r}
## download from  https://www.kaggle.com/saraabdelaal/abtestdata?select=ab_data.csv 

##load data into R 

data <- read.csv(file.choose())

```



## Data exploration and preperation and Wrangling 
```{r}
View(data)

head(data)

names(data)

summary(data)

length(unique(data$user_id))

## find the accounts with both test and control experiences these are issue users and they are excluded 

data_dups <- data %>% group_by(user_id) %>% summarise(counts = length(timestamp)) %>% filter(counts >1)

### exclude duplicate users 
data <- data %>% filter(!user_id %in% data_dups$user_id)

##extract date from time stamp 
data <- data %>% mutate(Test_Date = date(timestamp))

```


## Data analysis and Visulization
```{r}

##CVR trend chart for understanding performance over the days 
data %>% group_by(Test_Date, group) %>% summarise(converted = sum(converted),
                                                                counts =n(),
                                                                CVR = percent(sum(converted/n()))) %>%
 filter(converted >= 485L & converted <= 860L) %>%
 ggplot() +
  aes(x = Test_Date, y = converted, colour = group) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  labs(x = "Test Date", y = "CVR", title = "CVR Trend") +
  theme_minimal()

## CVR Box Plot for understanding limits and data spread 

data %>% group_by(Test_Date, group) %>% summarise(converted = sum(converted),
                                                                counts =n(),
                                                                CVR = percent(sum(converted/n()))) %>%
 filter(converted >= 490L & converted <= 860L) %>%
 ggplot() +
  aes(x = group, y = CVR, fill = group) +
  geom_boxplot() +
  scale_fill_hue(direction = 1) +
  labs(title = "CVR Box Plot") +
  theme_minimal()


## Density plot 

data %>% group_by(Test_Date, group) %>% summarise(converted = sum(converted),
                                                                counts =n(),
                                                                CVR = percent(sum(converted/n())))  %>%
 filter(converted >= 450L & converted <= 860L) %>%
 ggplot() +
  aes(x = CVR, fill = group, colour = group) +
  geom_density(adjust = 1L) +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  labs(title = "Density Plot") +
  theme_minimal()

```


## AB Test reults and statistics 
```{r}

Test_Results <- data %>% group_by(group) %>% summarise(converted = sum(converted),
                                                                counts =n(),
                                                                CVR =percent(sum(converted/n())))

CVR_lift <-  percent((((data%>%  summarise(t_sales = mean(case_when(group == "treatment" ~ converted), na.rm=TRUE)))/
(summarise(data,c_sales = mean(case_when(group == "control" ~ converted), na.rm=TRUE))))-1),2)



## prop.test() for proportions 
prop.test(x = c(Test_Results[Test_Results$group=="control",]$converted, Test_Results[Test_Results$group=="treatment",]$converted ), 
          n = c(Test_Results[Test_Results$group=="control",]$counts , Test_Results[Test_Results$group=="treatment",]$counts ), 
          alternative = "two.sided")

```






